Global code motion of congruent instructions

### 2017-06-10 paper.tex
corr

\subsubsection{Legality of sinking expressions}
\label{subsec:legality-sink}
Sometimes, hoisting is not upward-safe \cite{click1995global}, e.g., if the
expressions are in a landing pad, sinking of those expressions
may reduce code size. Sinking may also reduce the register pressure in some
cases, e.g., when the use operands are not kills. For sinking, higher ranked
expressions would be sunk first. And it would be illegal to sink higher ranked
identical expressions if they are not anticipable in the common
post-dominator. For example:

@@

In this example (c1, c2) or (d1, d2) are potential sinkable candidates. Since
(c1, c2) depend on i1 and i2 respectively which are also in their original basic
blocks, c1 and c2 are not anticipable in B3. So without knowing the ability to sink
of `i1' and `i2' it would be illegal to sink (c1, c2) to B3. On the other hand
(d1, d2) can safely be sunk because their operands are readily available at the
sink point, i.e., B3. It should also be noted that, just because the expressions
are identical and operands are available, it still requires a unique
post-dominating PHI to use the exact same values to be legally sinkable.

A general global scheduling algorithm also requires checks for undefined values
when introducing a new computation along a path. Since only very busy
expressions are moved in the current implementation, there is no need to check
for undefined resulting due to movement of instructions. This simplifies the
implementation.

>>>>

\subsubsection{Legality of sinking expressions}
\label{subsec:legality-sink}
Sometimes, hoisting is not upward-safe \cite{click1995global}, e.g., if the
expressions are in a landing pad, sinking of those expressions
may reduce code size. Sinking may also reduce the register pressure in some
cases, e.g., when the use operands are not kills. For sinking, higher ranked
expressions would be sunk first. And it would be illegal to sink higher ranked
identical expressions if they are not fully anticipable in the common
post-dominator. For example:

@@

In this example (c1, c2) or (d1, d2) are potential sinkable candidates. Since
(c1, c2) depend on i1 and i2 respectively which are also in their original basic
blocks, c1 and c2 are not fully anticipable in B3. So without knowing the ability to sink
of `i1' and `i2' it would be illegal to sink (c1, c2) to B3. On the other hand
(d1, d2) can safely be sunk because their operands are readily available at the
sink point, i.e., B3. It should also be noted that, just because the expressions
are identical and operands are available, it still requires a unique
post-dominating PHI to use the exact same values to be legally sinkable.

A general global scheduling algorithm also requires checks for undefined values
when introducing a new computation along a path. Since only very busy
expressions are moved in the current implementation, there is no need to check
for undefinedness resulting due to movement of instructions. This simplifies the
implementation.
